### 2016-12-12 paper/evaluation.tex
text from RQ2

\Fix{To evaluate how often developers use low-level parallelism, we
considered 216 Maven projects and analyzed \Fix{x} configurations
files. For each subject, we parsed all \emph{pom.xml} files from the
project (including submodules) and searched for all \emph{surefire}
settings on each XML file. Figure \Fix{...} illustrates how a
developer can explore parallelism via Surefire settings.}

>>>>

To evaluate the  use of low-level parallelism, we considered the
subjects from the groups \emph{long} and \emph{medium} identified in
Section~\ref{sec:rqone}. In an initial exploration, we searched for
evidences of low-level parallelism settings on configuration files
(\ie, \emph{pom.xml}) from each subject (\emph{long} and \emph{medium}
groups). Initially, our script finds recursively all \emph{pom.xml}
files from the project directory. For each file, we use the
command-line tool \emph{grep} to highlight the presence of the
keywords \emph{forkMode}, \emph{forkCount}, and \emph{parallel}. Any
of these keywords are present in all possible parallel settings (see
Section~\ref{sec:modes}).  We discovered that \Fix{X}\% and \Fix{y}\%
of subjects (\emph{long} and \emph{medium}, respectively) did not have
any evidence of low-level parallelism. It is important to mention that
this result an upper bound limit since the keyword highlighted could
not be part of a real configuration (\eg, part of a comment). To
investigate further the projects reported by our script, we manually
inspected \Fix{X} configuration files to eliminate false-positives.
\Fix{...elaborate...}
